---
title: "Chocolate Chip Cookies"
execute:
  error: true
author: "Your Name"
output: html_document
---

## Reading In the Data

First, read in the CSV data of cookie ingredients. Make sure that your end-result data has appropriate types for each column - these should match the types provided in the documentation in the README.md file.

```{r}
cdata<- read.csv("choc_chip_cookie_ingredients.csv")
```

```{python}
import pandas as pd

cdata = pd.read_csv('choc_chip_cookie_ingredients.csv')
```

## Exploratory Data Analysis

Exploratory data analysis is the process of getting familiar with your dataset. To get started, [this blog post](https://www.mrdbourke.com/a-gentle-introduction-to-exploratory-data-analysis/) provides a nice checklist to get you thinking:

> 1.  What question(s) are you trying to solve (or prove wrong)?
> 2.  What kind of data do you have and how do you treat different types?
> 3.  What's missing from the data and how do you deal with it?
> 4.  Where are the outliers and why should you care about them?
> 5.  How can you add, change or remove features to get more out of your data?

### Generating Questions

Generate at least 5 questions you might explore using this database of cookie ingredients.

1.Is there any missing data 2.How big at the disparities in ingredient quantity accross recipes. 3.Do they have different measurement types 4.How the ingredients affects the rating 5.Correlation between ingredient amount and rating list

### Skimming the Data

One thing we often want to do during EDA is to examine the quality of the data - are there missing values? What quirks might exist in the dataset?

The `skimr` package in R, and the similar `skimpy` package in python (which has a much better name, in my opinion), can help provide visual summaries of the data.

Install both packages, and read the package documentation ([R](https://cran.r-project.org/web/packages/skimr/vignettes/skimr.html), [Python](https://pypi.org/project/skimpy/)).

\[Part 1\] Use each package and generate summaries of your data that require the use of at least some non-default options in each package's `skim` function.

```{r}
library("skimr")
skim(cdata)
```

```{python}
from skimpy import skim
skim(cdata)
```

\[Part 2\] Write 1-2 sentences about what you can tell from each summary display you generate. Did you discover anything new about the data?

In the first display, we can see the dimensions, but it can also tell us how often specific column types occurs.

In the second display it reveals the character type columns as well as a summary showing max and min character length as well as unique, missing, and empty values.

In the third display it reveals the numeric type columns as well as a summary showing quartiles, deviation, mean, missing values, and histogram showing a visualization. From this we are able to gather that all columns besides Rating have no missing values and rating has about half of its values missing.

### Generating Tables

Another useful technique for exploratory data analysis is to generate summary tables. You may want to use the `dplyr` package in R (`group_by` or `count` functions), as well as the `groupby` and `count` methods in Pandas. [Python example](https://sparkbyexamples.com/pandas/pandas-groupby-count-examples/), [R example](https://dplyr.tidyverse.org/reference/count.html)

\[Part 1\] Using R and Python, generate a table that shows what **proportion** of recipes contain each type of ingredient, for the most common 20 ingredients.

```{r}
library("dplyr")

cdata<- cdata |> group_by(Ingredient)
Index<- distinct(cdata, Recipe_Index)


pcdata<- count(Index, Ingredient)
pcdata<- pcdata |> arrange(desc(n)) 
pcdata<- ungroup(pcdata) |> slice_max(order_by=n, n=20)

pcdata |> group_by(Ingredient) |> summarize(proportion = n/length(unique(Index$Recipe_Index)))
```

```{python}
import pandas as pd

pcdata = (
    cdata[['Ingredient', 'Recipe_Index']]
    .drop_duplicates()
    .groupby('Ingredient')
    .size()
    .nlargest(20)
    .reset_index(name='n')
)

pcdata['proportion'] = pcdata['n'] / cdata['Recipe_Index'].nunique()

table_pcdata = pcdata.groupby('Ingredient').agg(
  proportion=('proportion', 'max')
)

print(table_pcdata)
```

\[Part 2\] Print out a character string that lists all of the ingredients that do not appear in at least 20 recipes.

```{r}
library(stringr)
library(dplyr)
cdata<- cdata |> group_by(Ingredient)
Index2<- distinct(cdata, Recipe_Index)


pcdata2<- count(Index2, Ingredient)
pcdata2<- ungroup(pcdata2) |> filter(n < 20) 
strcdata2<- pcdata2$Ingredient 
strcdata2<- str_flatten(strcdata2, ", ")
strcdata2
```

```{python}
import pandas as pd

pcdata2 = (
    cdata[['Ingredient', 'Recipe_Index']]
    .drop_duplicates()
    .groupby('Ingredient')
    .size()
    .reset_index(name='n')
)

pcdata2 = pcdata2[(pcdata2['n']<20)]



print(pcdata2['Ingredient'])

```

### Visualization

Using whatever plotting system you are comfortable with in R or python, see if you can create a couple of useful exploratory data visualizations which address one of the questions you wrote above - or another question which you've come up with as you've worked on this assignment.

\[Part 1\] Create at least one plot (it doesn't have to be pretty) that showcases an interesting facet of the data.

```{r}
library("ggplot2")


ggplot(cdata, aes(Rating, color=cdata$Ingredient)) + geom_freqpoly(bins = 40)
```

\[Part 2\] Write 2-3 sentences about what you can learn from that plot and what directions you might want to investigate from here.

From the graph we can gather how often each of the top ingredients occur at each of ratings. With this we can find what ingredients are often seen a higher approval rating.
